---
title: "Homework #1 DACSS690"
author: "Annabel Smith"
output: 
  flexdashboard::flex_dashboard:
    navbar:
      - { title: "GitHub", icon: "fa-github", href: "https://github.com/DACSS690D-SpatialAnalysis/Homework1", align: right }
---

```{r setup, include=FALSE}
library(flexdashboard) # always
```

<!-- links -->
```{r}
ddmlink=
  ddm=url("https://github.com/DACSS690D-SpatialAnalysis/Homework1/raw/refs/heads/main/interactive_ddm.rds")

psmlink=
  psm=url("https://github.com/DACSS690D-SpatialAnalysis/Homework1/raw/refs/heads/main/interactive_psm.rds")

chorolink=
  choro=url("https://github.com/DACSS690D-SpatialAnalysis/Homework1/raw/refs/heads/main/interactive_choro.rds")
```

Sidebar {.sidebar}
=====================================

All three maps analyze the number of mobile phone subscribers in each country.

**Dot Density Map**

The number of dots in each country represents the *density* of mobile phone subscribers. Countries like Colombia and Ecuador have a higher density of mobile phones subscribers, represented by the denser cluster of red dots in those countries. Countries like Guyana, Suriname, or Uruguay, which have a noticeably smaller concentration of dots. 

**Proportional Symbols Map**

The size of the dot on each country represents the *number* of mobile phone subscribers. Brazil has the largest dot on this map, highlighting that they have the highest amount of mobile phone subscribers out of all the South American countries shown. One thing to note is that while Brazil has the largest number of subscribers, it does not have the highest density of subscribers as we already established with our DDM that Colombia has the highest density. 

Dot Density Map
===================================== 


### DDM of Mobile Phones in South America

```{r}
readRDS(ddm)
```


Proportional Symbols Map
===================================== 


### PSM of Mobile Phones in South America

```{r}
readRDS(psm)
```


Chloropleth Map
===================================== 


### Choropleth Map of Mobile Phones in South America

```{r}
readRDS(choro)
```

